Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-05-06 GWLDCII.tex
very minor edit to 3.4

We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $\{p_1, \ldots, p_r\}$ and $\{q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}
We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$. By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

@@

Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $p_r$ or $q_{r+1}$, and must therefore support some other propagator $t$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.  If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.  Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.

>>>>

We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and either:
\begin{itemize}
\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
  %a configuration \eqref{eq:2 prop config} in $D$
{\em or} 
\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}
We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$. By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

@@

Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.  If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.  Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.
